Output Summary

### 2023-09-08 03-post-process/ms-content/ms-content.Rmd
ms-content: force captions at top of figures

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    value: FALSE
  beta_fig:
    value: FALSE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
  surv_compare_fig:
    value: TRUE
  apportion_compare_fig:
    value: TRUE
  corr_compare_fig:
    value: TRUE
  WUL_change_fig:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage{float}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
editor_options: 
  chunk_output_type: console
---

>>>>

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    value: FALSE
  beta_fig:
    value: FALSE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
  surv_compare_fig:
    value: TRUE
  apportion_compare_fig:
    value: TRUE
  corr_compare_fig:
    value: TRUE
  WUL_change_fig:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{floatrow}
  - \floatsetup[figure]{style=plaintop}
  - \floatsetup[table]{style=plaintop}
editor_options: 
  chunk_output_type: console
---
